A Horrocks-type theorem for even orthogonal $K_2$

### 2019-09-20 dl-paper.tex
Fix misprint
Minor

After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see e.\,g.~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}). For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem. This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_{1,n}(k[x_1, \ldots x_n]) = \K_{1,n}(k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}. Suslin's results were subsequently generalized to $\K_1$-functors modeled on other linear groups (see the definition below). For example, for even-dimensional orthogonal groups the corresponding result was obtained by A.~Suslin and V. Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}. Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly} for the result over a field and ~\cite[Corollary~1.2]{St-Ded} for its further generalization to Dedekind domains of arithmetic type).

>>>>

After the original Serre problem had been solved, numerous analogous questions drew the attention of specialists (see e.\,g.~\cite{Su77, Su82, Abe83, Tu83, Lam10, St-poly, St-Ded}). For example, A.~Suslin formulated and solved the so-called $K_1$-analogue of Serre's problem. This result asserts that the functor $\K_{1,n}(R) = \mathrm{GL}_{n}(R)/\E_n(R)$ has the property $\K_{1,n}(k[x_1, \ldots x_n]) = \K_{1,n}(k) = k^\times$ for all fields $k$ and $n \geq 3$ see~\cite[Corollary~7.11]{Su77}. Suslin's results were subsequently generalized to $\K_1$-functors modeled on other linear groups (see the definition below). For example, for even-dimensional orthogonal groups the corresponding result was obtained by A.~Suslin and V. Kopeiko in~\cite{Su82}, while for more general types of Chevalley groups of rank $\geq 2$ this is a result of E.~Abe, see~\cite{Abe83}. Recently, A.~Stavrova has obtained probably the most general results in this direction: she solved the analogue of Serre problem for the functor $\K_1^G$ modeled on arbitary isotropic reductive group scheme $G$ of isotropic rank $\geq 2$ (see~\cite[Theorem~1.2]{St-poly}).
See also \cite[Corollary~1.2]{St-Ded} for the generalization of Abe's result to Dedekind domains of arithmetic type.
